Strotor: A Minimalistic Approach to \\ Exploring Hierarchical Data

### 2014-04-16 paper/paper.tex
...

No formal evaluation have been done yet, but {\ST} has been used in the author's
living room for six months, and the author's family members are using it
everyday for watching anime films and listening to music.
Besides PowerMate, a wireless mouse is preferred,
since we can carry the mouse anywhere and select
a film or a music just by rotating the mouse wheel.

We displayed {\ST} at an exhibition
held in November 2013, and asked more than 100 people to try it.
%
Since the only thing a user can do with {\ST} is to rotate the device,
users seemed to be able to understand the behavior of {\ST} with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the users, but the hard restriction of the device seems to have worked in this case.

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{Asking people to use Strotor at an exhibition. The subject is using PowerMate for browsing photos.}
\label{powermate}
\end{figure}

@@

We have developed a new very simple interaction method for exploring
large hierarchical data structure.
Using only one rotating device,

>>>>

No formal evaluation have been done yet, but {\ST} has been used in the author's
living room for six months, and the author's family members are using it
everyday for watching anime films and listening to music.
Besides PowerMate, a wireless mouse is preferred,
since we can carry a wireless mouse anywhere and select
a film or a music just by rotating the mouse wheel.

We displayed {\ST} at an exhibition
held in November 2013, and asked more than 100 people to try it
(Figure \ref{exhibition}).
%
Since the only thing a user can do with {\ST} is to rotate the device,
users seemed to be able to understand the behavior of {\ST} with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the subjects, but the hard restriction of the device seems to have worked in this case.

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People trying Strotor at an exhibition.}
\label{exhibition}
\end{figure}

@@

We have developed a new simple interaction method ``{\ST}'' for exploring
large hierarchical data structure.
{\ST} user can easily find an entry in a huge hierarchical database
only by using a rotating input device which can be installed at
wide range of locations where conventional keybords and switches do not fit.
We are hoping to try various implementations of {\ST} and try them at
various places like kitchens, restrooms, etc.
